Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-07 vesicle_code/docs/adhesion/adhesion.tex
added figures for fig 17
finished up some edits

Future work includes three dimensional simulations, viscosity contrast,
dense suspensions, and confined suspensions.
Figure~\ref{fig:relaxationManyVes} illustrate snapshots of five vesicles
suspended inside of a larger vesicle.  There is no imposed flow, so the
dynamics are governed entirely by the adhesion, bending, and tension
forces.  In the absence of confinement, we would expect the vesicles to
align themselves as a rouleaux with the membranes forming a parachute,
male-female, or S-shape
configurations~\cite{FlormannAouane2017_SciReports}.  However, because
of the bounding vesicle and the dense packing, the interior vesicles
align themselves differently.  In addition, several parts of the
bounding membrane closely follow the interior membranes in order to
minimize the adhesion energy.  In
Figure~\ref{fig:relaxationManyVesAdhesionTension} we plot the tension
(left) and adhesion (right) of the final equilibrium configuration.

@@

\begin{figure}[htp]
\todo[inline]{Figures of tension and adhesion of the final
configuration}
\caption{\label{fig:relaxationManyVesAdhesionTension} Something smart to
say ....}
\end{figure}

@@

YNY would like to acknowledge helpful discussions with blah blah blah.
YNY acknowledges support from NSF-DMS 1614863 and 1412789, and Flatiron
Institute, part of the Simons Foundation.

>>>>

Future work includes three dimensional simulations, viscosity contrast,
dense suspensions, and confined suspensions.
Figure~\ref{fig:relaxationManyVes} illustrate snapshots of five vesicles
suspended inside of a larger vesicle.  There is no imposed flow, so the
dynamics are governed entirely by the adhesion, bending, and tension
forces.  In the absence of confinement, we would expect the vesicles to
align themselves as a rouleaux with the membranes forming a parachute,
male-female, or S-shape
configurations~\cite{FlormannAouane2017_SciReports}.  However, because
of the bounding vesicle and the dense packing, the interior vesicles
align themselves differently.  In addition, several parts of the
bounding membrane closely follow the interior membranes in order to
minimize the adhesion energy.  In
Figure~\ref{fig:relaxationManyVesAdhesionTension} we plot the tension
(left) and adhesion (right) of the final equilibrium configuration.
Both the vesicle shape, tension, and adhesion qualitatively agree with
our doublet results.  In particular, the interior vesicles form a flat
contact region with a large negative tension.

@@

\begin{figure}[htp]
\centering
\includegraphics[height=0.4\textwidth]{figs/relaxationManyVesTension.png}
\includegraphics[height=0.4\textwidth]{figs/relaxationManyVesAdhesion.png}
\caption{\label{fig:relaxationManyVesAdhesionTension} The tension ({\em
left}) and adhesion force ({\em right}) of the final configuration from
Figure~\ref{fig:relaxationManyVes}.  Along the bounding vesicle, the
tension is largest and the adhesion is smallest in the regions that are
well-separated from the interior vesicles.  Similar to other
simulations, the interior vesicles are relatively flat and have a large
negative tension in the contact regions.}
\end{figure}

@@

YNY would like to acknowledge helpful discussions with blah blah blah.
YNY acknowledges support from NSF-DMS 1614863 and 1412789, and Flatiron
Institute, part of the Simons Foundation.  BQ acknowledges support from
Florida State University startup funds and Simons Foundation Mathematics
and Physical Sciences-Collaboration Grants for Mathematicians 527139.
